Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-11 manuscript.tex
responded to/revised some comments

The standard errors were also computed for each CCF parameter for all the CCFs of HD215152, HD192310 and Corot-7. \jessi{Why weren't the others stars included?} \umberto{because the computational time for Tau Ceti and Alpha Cent was much longer (there are much more CCF's). can we add the the SNR 'levels' are covered with the stars we used?}
This provides information on how the noise of each CCF parameter varies as a function of SNR, where the SNR measured at 550 nm on the original spectra varies between 10 and 500. 
The combined results for all the stars considered are displayed in Fig.~\ref{fig:se}. 
The top plots show the standard errors of the three different estimated RV's, the width, and the asymmetry estimates. 
Note that because BIS SPAN and $\gamma$ do not have the same units, the estimated slopes of the correlation between those two parameters to transform $\gamma$ in \ms were used (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star). 
In the bottom plots show the ratio between the standard errors measured when using the SN parameters and the Normal parameters. Values smaller or larger than one will imply that standard errors from the SN parameters are more or less precise than the Normal parameters, respectively.

@@

Similar conclusions were reached with the real data as with the results of the SOAP 2.0 simulations regarding the strength of the correlation between the CCF asymmetry and the RV, as well as between the CCF width and the RV. 
However, the simulated data stronger asymmetry-RV correlation between $\gamma$ and SN median RV while the real data had stronger correlations between $\gamma$ and SN mean RV. 
There could be several reasons for this difference. First, it may be due to the fact that in SOAP 2.0 uses a variation of a spot template spectrum as the model rather than a facula template spectrum so the SOAP spectra with a facula is not accurately modeling this type of activity. Because the temperature between a spot and a faculae is significantly different, their spectra should be different. 
Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region. 
These reasons could also be responsible for the general differences observed in the behavior of the mean and the median of the SN between the SOAP 2.0 data and real data. \jessi{regarding the previous statement, would you say that there are also difference in the N mean RV generally between the SOAP and real data?  I wonder if that could somehow be tied in? }
Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are generally more sensitive to activity than the parameters derived from the Normal.  Also, the correlation between the asymmetry and the SN mean RV is always stronger than the parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}. Since if an apparent RV signal is induced by activity generally a strong correlation will be observed between the RV and the FWHM of the CCF or its BIS SPAN, to use the SN density to fit the CCF leads to a better understanding of the spurious variations in RV caused by stellar activity.

>>>>

The standard errors were also computed for each CCF parameter for all the CCFs of HD215152, HD192310 and Corot-7. \jessi{Why weren't the others stars included?} \umberto{because the computational time for Tau Ceti and Alpha Cent was much longer (there are much more CCF's). can we add the the SNR 'levels' are covered with the stars we used?}
\jessi{How much longer would it take to include these?  Can we run them on an HPC?  At the very least we should note why they are not included}
This provides information on how the noise of each CCF parameter varies as a function of SNR, where the SNR measured at 550 nm on the original spectra varies between 10 and 500. 
The combined results for all the stars considered are displayed in Fig.~\ref{fig:se}. 
The top plots show the standard errors of the three different estimated RV's, the width, and the asymmetry estimates. 
Note that because BIS SPAN and $\gamma$ do not have the same units, the estimated slopes of the correlation between those two parameters to transform $\gamma$ in \ms were used (see Fig.~\ref{fig:alphacent:corr.gamma} and Table~\ref{table:summaryStars} for the value of the slope for each star). 
In the bottom plots show the ratio between the standard errors measured when using the SN parameters and the Normal parameters. Values smaller or larger than one will imply that standard errors from the SN parameters are more or less precise than the Normal parameters, respectively.

@@

Similar conclusions were reached with the real data as with the results of the SOAP 2.0 simulations regarding the strength of the correlation between the CCF asymmetry and the RV, as well as between the CCF width and the RV. 
However, the simulated data stronger asymmetry-RV correlation between $\gamma$ and SN median RV while the real data had stronger correlations between $\gamma$ and SN mean RV. 
There could be several reasons for this difference. First, it may be due to the fact that in SOAP 2.0 uses a variation of a spot template spectrum as the model rather than a facula template spectrum so the SOAP spectra with a facula is not accurately modeling this type of activity. Because the temperature between a spot and a faculae is significantly different, their spectra should be different. 
Additionally, there are expected to be multiple active regions on a star at different locations in longitude and latitude, while the SOAP 2.0 data used in the simulation study included only a single active region. 
These reasons could also be responsible for the general differences observed in the behavior of the mean and the median of the SN between the SOAP 2.0 data and real data. \jessi{regarding the previous statement, would you say that there are also differences in the N mean RV generally between the SOAP and real data?  I wonder if that could somehow be tied in? }
Nevertheless, in both the simulated and the real cases, the parameters derived from the SN are generally more sensitive to activity than the parameters derived from the Normal.  Also, the correlation between the asymmetry and the SN mean RV is always stronger than the parametrization of the CCF presented in \citet{Boisse-2011} and \citet{Figueira-2013}. Since if an apparent RV signal is induced by activity generally a strong correlation will be observed between the RV and the FWHM of the CCF or its BIS SPAN, to use the SN density to fit the CCF leads to a better understanding of the spurious variations in RV caused by stellar activity.
